%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Solution Engineer} % Job title
    {VMware} % Organization
    {Barcelona, Spain} % Location
    {Jul. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Talking to customers, introducing them to new technology concepts and ideas that can enhance their business strategy.}
        \item {Presenting and demonstrating transformative VMware technologies that can make their strategic vision a reality. Designing the right technology solutions to meet customers' biggest business challenges, taking advantage of a rich portfolio of VMware products and services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tanzu Solution Engineer Intern} % Job title
    {VMware} % Organization
    {Paris, France} % Location
    {Mar. 2022 - Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analysis of the VMware Tanzu product portfolio.}
        \item {Build a Cloud Native application using an Agile approach.}
        \item {Continuous Integration and Deployment of the application on different targets: Local, Docker, Kubernetes.}
        \item {Develop and deliver presentations and demonstrations of product and solution onsite and remotely.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Engineering Intern} % Job title
    {Formalearning} % Organization
    {Lyon, France} % Location
    {May. 2021 - Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Creation of multilingual interface to a training platform for the self-registration of learners.}
        \item {Realization of automation for database reconciliation, for the marketing of data and analysis of the profitability of the project.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
